Data-Driven Modelling \& \\ Forecasting of Chaotic Systems

### 2022-01-18 projectReport/chapter3.tex
M final edits to Ch.5 and Michelle edits up to Ch.4

First we establish the method of Takens delay embedding. 
In this method, one considers a discrete-time dynamical system defined on a `nice' space (a smooth manifold)\ednote{B: Should this be further explained?} that can be obtained as time-$K$ map of a continuous time-dynamical system, concepts formalised below.
We make observations from such a system, i.e., we observe the evolution of $\theta(w_0)$ (where $w_0$ represents the initial state) by examining  a finite set of values of $u_n :=  \theta(w_n) = \theta(Tw_{n-1})$. The sequence $\{u_n\}$ represents a scalar time-series and intuitively $\theta$ represents a probe inserted into a bigger system which is itself only measuring/extracting a small part of the greater system state at time $t=n$. 
Consider, for example, a thermometer erected to measure the ambient temperature in a local village. This measurement function, the thermometer, is capturing only a single aspect, the temperature, of a much grander dynamical system entailing the current weather of the surrounding area. Even more than that though- it is measuring a miniscule part of the global weather system.

@@

We define first the concepts of homeomorphism and embedding:
\begin{Definition}\rm
  {\bf(Homeomorphism)}\label{Dfn_homeo}\rm
  A homeomorphism is a function $f:Z\rightarrow Y$ between two topological spaces $Z$ and $Y$ that is continuous, bijective and has a continuous inverse. 
\end{Definition}

@@

Takens Theorem states a result establishing a relationship between the observed and underlying dynamical systems by showing that the concatenation of a sufficiently large number of previous observations into a vector will, under certain conditions, generate a map between the vectors from the respective systems.  We formulate the theorem from~\cite{takens1981detecting}.

\begin{Theorem} 
	[\bf Takens Embedding Theorem (adopted from~\cite{takens1981detecting})]\label{Thm_Takens}
         Let $W$ be a compact manifold of dimension $m$, and $d\ge m$ so that $2d$ is an integer. It is a 
            generic property for the pair $(T, \theta)$,  where $T:W \to W$ is
            a smooth diffeomorphism, and $\theta:W \to \mathbb{R}$ a smooth function, the map $\Phi_{2d,\theta}:W \to \mathbb{R}^{2d+1}$ defined on $W$ by 
            $\Phi_{2d,\theta}(w) := (\theta(T^{-2d}w)\ldots,\theta(T^{-1}w),\theta(w))$
            is a diffeomorphic embedding; by `smooth' we mean at least $C^2$. Consequently, there exists a map $F_\theta: \Phi_{2d,\theta}(W) \to \Phi_{2d,\theta}(W)$ defined by \[F_\theta: (\theta(T^{-2d}w),\ldots,\theta(T^{-1}w),\theta(w)) \mapsto 
            (\theta(T^{-2d+1}w),\ldots,\theta(w),\theta(Tw)) \]
           so that $(W,T)$ is topologically conjugate to 
            $(\Phi_{2d,\theta}(W), F_\theta)$.    
\end{Theorem}

By generic we mean a residual set on a certain topology on appropriate spaces of functions (that we do not describe here) \ednote{B: Where can I find a citation for this?}. 
By $C^2$, we make reference to a twice-differentiable function  with a continuous second derivative. In our scenario (and this remains important throughout) the input space $U$ is considered the attractor.~\label{attractor_U}

@@

This requirement is not overly restrictive, as a great number of chaotic systems do have a surjective map. (Cite) \ednote{B:I remember you saying this in one of our sessions, but don't have a source for it. Do you have a specific reference?}

>>>>

First we establish the method of Takens delay embedding. 
In this method, one considers a discrete-time dynamical system defined on a `nice' space (a smooth manifold)\ednote{B: Where can I find a citation for this?} that can be obtained as time-$K$ map of a continuous time-dynamical system, concepts which are formalised below.
We make observations from such a system, i.e., we observe the evolution of $\theta(w_0)$ (where $w_0$ represents the initial state) by examining  a finite set of values of $u_n :=  \theta(w_n) = \theta(Tw_{n-1})$. The sequence $\{u_n\}$ represents a scalar time-series and intuitively $\theta$ represents a probe inserted into a bigger system which is itself only measuring/extracting a small part of the greater system state at time $t=n$. 
Consider, for example, a thermometer erected to measure the ambient temperature in a local village. This measurement function, the thermometer, is capturing only a single aspect, the temperature, of a much grander dynamical system entailing the current weather of the surrounding area. Even more than that though- it is measuring a miniscule part of the global weather system.

@@

We define first the concepts of homeomorphism and embedding:
\begin{Definition}
  {\bf(Homeomorphism)}\label{Dfn_homeo}\rm
  A homeomorphism is a function $f:Z\rightarrow Y$ between two topological spaces $Z$ and $Y$ that is continuous, bijective and has a continuous inverse. 
\end{Definition}

@@

Takens Theorem states a result establishing a relationship between the observed and underlying dynamical systems by showing that the concatenation of a sufficiently large number of previous observations into a vector will, under certain conditions, generate a map between the vectors from the respective systems.  We formulate the theorem from~\cite{takens1981detecting} after establishing preliminary definitions.

\ednote{It was suggested that I define these two concepts before stating the theorem.}
\begin{Definition}
  [\bf{Manifold, Compact Manifold}]\label{Dfn_compactManif}\rm
  A topological space is called a manifold if every point in the space has a neighbourhood homeomorphic to $\mathbb{R}^n$. Succinctly, a manifold is a locally Euclidean topological space.
  If a manifold is compact as a space topologically, then it is termed a compact manifold
\end{Definition}

\begin{Definition}
  [\bf{Diffeomorphism}]\label{Dfn_diffeo}\rm
  A smooth, differential map $f:X\to{Y}$ with a differentiable inverse is said to be a diffeomorphism. By `smooth' we mean at least $C^2$, where $C^2$ refers to any twice-differentiable function  with a continuous second derivative.
\end{Definition}

\begin{Theorem} 
	[\bf Takens Embedding Theorem (adopted from~\cite{takens1981detecting})]\label{Thm_Takens}
         Let $W$ be a compact manifold of dimension $m$, and $d\ge m$ so that $2d$ is an integer. It is a 
            generic property for the pair $(T, \theta)$,  where $T:W \to W$ is
            a smooth diffeomorphism, and $\theta:W \to \mathbb{R}$ a smooth function, the map $\Phi_{2d,\theta}:W \to \mathbb{R}^{2d+1}$ defined on $W$ by 
            $\Phi_{2d,\theta}(w) := (\theta(T^{-2d}w)\ldots,\theta(T^{-1}w),\theta(w))$
            is a diffeomorphic embedding. Consequently, there exists a map $F_\theta: \Phi_{2d,\theta}(W) \to \Phi_{2d,\theta}(W)$ defined by \[F_\theta: (\theta(T^{-2d}w),\ldots,\theta(T^{-1}w),\theta(w)) \mapsto 
            (\theta(T^{-2d+1}w),\ldots,\theta(w),\theta(Tw)) \]
           so that $(W,T)$ is topologically conjugate to 
            $(\Phi_{2d,\theta}(W), F_\theta)$.    
\end{Theorem}

By generic, we mean a residual set on a certain topology on appropriate spaces of functions (that we do not describe here) \ednote{B: Where can I find a citation for this?}. 
In our scenario (and this remains important throughout) the input space $U$ is considered the attractor.~\label{attractor_U}

@@

This requirement is not overly restrictive, as a great number of chaotic systems do have a surjective map. \textbf{(Cite)} \ednote{B: I remember you saying this in one of our sessions, but don't have a source. Could you point me to a resource?}

### 2022-01-18 projectReport/chapter4.tex
checkpoint
M final edits to Ch.5 and Michelle edits up to Ch.4

In this chapter, we discuss results on the mapping of temporal data obtained from a discrete-dynamical system onto a different space through the notion of a driven dynamical system. 
We also consider the conditions a driven system should possess to avoid adding distortion to its state-space representation. We then describe the \emph{single-delay dynamics} (SDD) of the system and finally recall conditions on the driven system so that the SDD are conjugate (or at least semi-conjugate) to the underlying system. 
The SDD can then be used to forecast and reconstruct the underlying system.

@@

\begin{Definition}
  [\bf Nonautonomous Dynamical System (adopted from~\cite{Manju_ESP})]\label{Dfn_NDS}\rm
  A nonautonomous dynamical system (NDS) on a space $X$ is simply a dynamical system comprising a family of maps ${\{g_n\}}_{n \in \mathbb{Z}}$ where $g_n(\ldotp):=g(u_n,\ldotp):X\to{X}$ is continuous. Each $g_n$ arises as a consequence of an input $u_n$ from the input space $U$, a topological space. 
\end{Definition}

@@

The reachable set itself can defined independently from $g$ possessing the ESP/USP. Note that $x\in{X_n(\overline{u})}$ if and only $g$ has a solution $\{x_k\}$ for $x_n=x$ and input $\overline{u}$, a result proved in nonautonomous dynamical systems literature~\cite{manjunath2014dynamics, manjunath2013echo}. \ednote{B: Adjusted sentence and cited}

@@

\begin{Theorem}\label{Thm_CompactExistence}
 Let $g$ be a driven system.  If $X$ is compact then for each input $\overline{u}$, there exists at least one solution to the driven system $g(\ldotp, x)$
\end{Theorem}
{\bf Proof.} May be found in~\cite{kloeden2011nonautonomous, manjunath2014dynamics, manjunath2013echo}
% One may easily construct many systems with trivial solution-sets, such as $g(u,x)=x$ which has only the constant solution $x$ and so for $U=[-1,1]$, the system would have no solution if $|x|>1$. To refine the scenario, we consider only systems with unique solutions. 
\section{Unique Solution Property}

@@

 \begin{Theorem}
  For a compactly driven system, a causal mapping $H$ exists if and only if $g$ has the USP. 
\end{Theorem}
{\bf Proof.}  See~\cite[Th.3]{manjunath2013echo}.

The driven system $g$ can induce an embedding of $\overleftarrow{U}$ in $\overleftarrow{X}$ as follows: 
If the causal mapping $H:\overleftarrow{U}{\to}{\overleftarrow{X}_U}$ is injective (in addition to being surjective), it becomes the embedding of $\overleftarrow{U}$ in $\overleftarrow{X}$ induced by the driven system $g$. 
The continuity of $H^{-1}$ follows from the fact that $H$ is itself a continuous and surjective mapping of a compact space $\overleftarrow{U}$ in a Hausdorff space.
and we refer to the map $H$ as a \emph{causal embedding}. 
\ednote{B: edited the sentence here}

When $g$ has the USP, the diagram below (adopted from~\cite{Manju_Nonlinearity}) illustrates the operation of the mappings $h$ and $H$. The mapping $h:\overleftarrow{U}\to{X_U}$ is also considered an observable as mentioned in the introduction of Chapter~\ref{ch3}).

@@

The inverse-limit space is well-defined since $T : U \to{U}$ is surjective by assumption.
We now get to the concept of embedding the inverse limit-space of the dynamical system in $X \times X$. 
\begin{Definition} \rm
	We say a driven system $g$ \emph{causally embeds} a dynamical system $(U,T)$ if it satisfies the two properties: (i) a universal semi-conjugacy exists and  (ii)  $H_2(\cev{u}) := (h(r\cev{u}),h(\cev{u}))$ embeds the inverse-limit space $\widehat{U}_T$ in $X \times X$. \end{Definition}

  It is imperative to take note of a subtlety here: we refer to the \emph{map} $H$ as a (causal) embedding, whereas the driven \emph{system} $g$ (causally) embeds another \emph{system} $(U,T)$. \ednote{B: inserted line}

@@

So far it is not clear if the USP alone ensures the ability to causally embedding a dynamical system and we mention that a driving function $g$ cannot just be chosen in a frivolous manner. This could possibly complicate our work. %\ednote{B: Grammarly}

@@

%To achieve a causal embedding embedding not just a causal mapping, it is undesirable to choose a function $g$ that quenches the temporal structure in $u$ by contracting to such a degree that the ability to recover information from the original system is lost completely.
In the above example (\ref{ex_halfux}), the input's temporal variation could not be related to the reachable set as $X_U$ only consisted of a single element; little, if not no, information is encoded.
To obtain a suitably complex function $g$, it is thus desired that the reachable set of a driven system  be large enough to relate to the input. 
This is true even for embedding  the inverse-limit space of a dynamical system. \ednote{B: Expand or refer?}

@@

@@

\begin{Theorem}\label{Thm_GT_Exists}
  For an SI-invertible driven system $g$ and a dynamical system $(U,T)$, the map $G_T: Y_T \to Y_T$ defined by the relation $(x_{n-1},x_n) \mapsto (x_n,x_{n+1})$ is well-defined. 
  (This results holds even in the absence of $g$ possessing over the USP) 
  % Moreover, the mapping $(x_{n-1},x_n) \mapsto u_{n}$ is well-defined when $x_{n-1}$ and $x_n$ are successive points on a solution obtained for an input  $\{u_n\}$ that is an orbit of $T$.
  \end{Theorem}
  {\bf Proof.} See~\cite[Th.3]{Supp}

@@

The UAP guarantees that all trajectories will converge to the same trajectory as time moves forward. An illustration of this is shown in Fig.~\ref{fig:memloss_conttime} where the trajectory in red locks on to the supposed actual solution when the system has the USP.

\begin{figure}[ht]
  \includegraphics[scale=0.35]{Graphs/_Nonlinearity_Fig_response.eps}
  \centering
\captionof{figure}{A coordinate of a simulated solution $(x_0,x_1,\ldots,x_{5000})$ of a RNN  plotted in red (with parameter $\alpha=0.99$ where $g$ has the USP) and blue ($a=1$, $\alpha=1.05$ where $g$ does not have the USP) while the matrices $A$ and $B$ are randomly generated, and $B$ has unit spectral radius.  Reproduced from~\cite{Manju_Nonlinearity}. } 
\label{fig:memloss_conttime} 
\end{figure} 
\ednote{B: How can I explain the black line? I don't think this makes sense to the reader immediately.}

@@

\begin{Theorem}
  [\bf Causal Embedding Theorem (adopted from~\cite{Supp})]
  % {\bf (Causal Embedding Theorem.)}
\label{Thm_CET}
	Let $g$ be a driven system with SI-invertibility and the USP. Let $h$ denote the universal semi-conjugacy and $H_2(\overleftarrow{u}) := (h(r\overleftarrow{u}),h(\overleftarrow{u}))$, where $r$ is the right-shift map. 
 Let $(\widehat{U}_T, \widehat{T})$  be the inverse-limit system of a dynamical system $(U,T)$. 
 Then the restriction of $H_2$ to $\widehat{U}_T$ is a topological semi-conjugacy between the inverse-limit system $(\widehat{U}_T, \widehat{T})$ 
and the induced dynamical system  $(Y_T,G_T)$, i.e., the following diagram commutes
\begin{equation} \label{comm_H_CET}
\psset{arrows=->, arrowinset=0.25, linewidth=0.6pt, nodesep=3pt, labelsep=2pt, rowsep=0.7cm, colsep = 1.1cm, shortput =tablr}
 \everypsbox{\scriptstyle}
 \begin{psmatrix}
 \widehat{U}_T & \widehat{U}_T\\%
 Y_T &  Y_T.
 %%%
%  \ncline{1,1}{1,2}^{\widehat{T}} \ncline{1,1}{2,1} <{H_2}
%  \ncline{1,2}{2,2} > {H_2}
%  \ncline{2,1}{2,2}^{G_T}
 \end{psmatrix}
 \end{equation}
or in other words, $(Y_T, G_T)$ is a factor of  $(\widehat{U}_T, \widehat{T})$. Further, if $T:U \to U$ is a homeomorphism, 
then $H_2$ embeds $\widehat{U}_T$ in $X_U \times X_U$, and hence $(Y_T, G_T)$ is conjugate to $(\widehat{U}_T, \widehat{T})$.
\end{Theorem}
{\bf Proof.}  May be found as the proof of~\cite[Th.4]{Supp}

@@

\begin{figure}[ht]
  \includegraphics[scale=0.3]{Graphs/_summarypictorial.eps}
  \centering
  \captionof{figure}{Pictorial summary of results obtained up to now and how they overlap. Reproduced from \textbf{(Cite SIG-25May)} }
  \label{fig:pictorialSummary}
\end{figure}
\ednote{Ask M: Cite SIG-25May.}

@@

\begin{Theorem}
  When $x_n$ and $x_{n-1}$ are successive points on a solution obtained for input-orbit of $T$ $\{u_n\}$, then the map $\Gamma: X\times{X}\to{U}$ defined by $(x_{n-1},x_n)\mapsto{u_n}$ exists whenever $G_T$ exists 
\end{Theorem}
{\bf Proof.}  See~\cite[Th. 3c]{manjunath2021universal}.

@@

The graph in equation \ref{fig:comm_H_CET} is then extended to the diagram~\ref{Scomm_imp} below:

>>>>

In this chapter, we discuss mathematical results relating to the mapping of temporal data obtained from a discrete-dynamical system onto a different space through the notion of a driven dynamical system. 
We also consider the conditions a driven system should possess to avoid adding distortion to its state-space representation. We then describe the \emph{single-delay dynamics} (SDD) of the system and finally state conditions on the driven system so that the SDD are conjugate (or at least semi-conjugate) to the underlying system. 
The SDD can then be used to forecast and reconstruct the underlying system.

@@

\begin{Definition}
  [\bf Nonautonomous Dynamical System (as defined in~\cite{Manju_ESP})]\label{Dfn_NDS}\rm
  A nonautonomous dynamical system (NDS) on a space $X$ is simply a dynamical system comprising a family of maps ${\{g_n\}}_{n \in \mathbb{Z}}$ where $g_n(\ldotp):=g(u_n,\ldotp):X\to{X}$ is continuous. Each $g_n$ arises as a consequence of an input $u_n$ from the input space $U$, a topological space. 
\end{Definition}

@@

The reachable set itself can defined independently from $g$ possessing the ESP/USP. Note that $x\in{X_n(\overline{u})}$ if and only $g$ has a solution $\{x_k\}$ for $x_n=x$ and input $\overline{u}$, a result proved in nonautonomous dynamical systems literature~\cite{manjunath2014dynamics, manjunath2013echo}.

@@

\begin{Theorem}\label{Thm_CompactExistence}
 Let $g$ be a driven system.  If $X$ is compact then for each input $\overline{u}$, there exists at least one solution to the driven system $g(\ldotp, x)$
\end{Theorem}
\vspace{-6mm}
{\bf Proof.} May be found in~\cite{kloeden2011nonautonomous, manjunath2014dynamics, manjunath2013echo}
% One may easily construct many systems with trivial solution-sets, such as $g(u,x)=x$ which has only the constant solution $x$ and so for $U=[-1,1]$, the system would have no solution if $|x|>1$. To refine the scenario, we consider only systems with unique solutions. 
\section{Unique Solution Property}

@@

 \begin{Theorem}
  For a compactly driven system, a causal mapping $H$ exists if and only if $g$ has the USP. 
\end{Theorem}
\vspace{-6mm}
{\bf Proof.}  See~\cite[Th.3]{manjunath2013echo}.

The driven system $g$ can induce an embedding of $\overleftarrow{U}$ in $\overleftarrow{X}$ as follows: 
If the causal mapping $H:\overleftarrow{U}{\to}{\overleftarrow{X}_U}$ is injective (in addition to being surjective), it becomes the embedding of $\overleftarrow{U}$ in $\overleftarrow{X}$ induced by the driven system $g$. 
The continuity of $H^{-1}$ follows from the fact that $H$ is itself a continuous and surjective mapping of a compact space $\overleftarrow{U}$ in a Hausdorff space.
and we refer to the map $H$ as a \emph{causal embedding}. 
%\ednote{B: edited the sentence here}

When $g$ has the USP, the diagram below (taken from~\cite{Manju_Nonlinearity}) illustrates the operation of the mappings $h$ and $H$. The mapping $h:\overleftarrow{U}\to{X_U}$ is also considered an observable as mentioned in the introduction of Chapter~\ref{ch3}).

@@

The inverse-limit space is well-defined since $T : U \to{U}$ is surjective by assumption.
We now get to the concept of embedding the inverse limit-space of the dynamical system in $X \times X$. 
\begin{Definition} \rm
	We say a driven system $g$ \emph{causally embeds} a dynamical system $(U,T)$ if it satisfies the two properties: 
  \vspace{-8mm}
\begin{enumerate}[noitemsep, label=\roman*.]
  \item  a universal semi-conjugacy exists and  
  \item  $H_2(\cev{u}) := (h(r\cev{u}),h(\cev{u}))$ embeds the inverse-limit space $\widehat{U}_T$ in $X \times X$. 
\end{enumerate}
\end{Definition}

It is imperative to take note of a subtlety here: we refer to the \emph{map} $H$ as a (causal) embedding, whereas the driven \emph{system} $g$ (causally) embeds another \emph{system} $(U,T)$. \ednote{Check this sentence again.}

@@

So far it is not clear whether the USP alone ensures the ability to causally embedding a dynamical system and we mention that a driving function $g$ cannot just be chosen in a frivolous manner. This could possibly complicate our work. %\ednote{B: Grammarly}

@@

%To achieve a causal embedding embedding not just a causal mapping, it is undesirable to choose a function $g$ that quenches the temporal structure in $u$ by contracting to such a degree that the ability to recover information from the original system is lost completely.
In the above example (\ref{ex_halfux}), the input's temporal variation could not be related to the reachable set as $X_U$ only consisted of a single element; little, if not no, information is encoded.
To obtain a suitably complex function $g$, it is thus desired that the reachable set of a driven system  be large enough to relate to the input. 
This is even true for embedding  the inverse-limit space of a dynamical system. \ednote{B: Expand or refer?}

@@

As mentioned, $g$ can also introduce additional complexity to a solution. Consider the Figure~\ref{fig:memloss_conttime} where a RNN's solution was numerically simulated for randomly generated matrices $A$ and $B$ where $B$ has unit spectral radius.
An input sequence (black) $(x_0,x_1,\ldots,x_{5000})$ was fed to the network and we plot it as well as the the coordinates of two simulated solutions in red (with parameter $a=1$, $\alpha=0.99$ where $g$ has the USP) and blue ($a=1$, $\alpha=1.05$ where $g$ does not have the USP).
The red solution mimics the input sequence well in its variation, whereas the blue solution is disordered and changes a lot. In this we may say that the blue solution has introduced additional complexity to the system.  \ednote{B: Added this paragraph}

@@

\begin{Theorem}\label{Thm_GT_Exists}
  For an SI-invertible driven system $g$ and a dynamical system $(U,T)$, the map $G_T: Y_T \to Y_T$ defined by the relation $(x_{n-1},x_n) \mapsto (x_n,x_{n+1})$ is well-defined. 
  (This results holds even in the absence of $g$ possessing over the USP) 
  % Moreover, the mapping $(x_{n-1},x_n) \mapsto u_{n}$ is well-defined when $x_{n-1}$ and $x_n$ are successive points on a solution obtained for an input  $\{u_n\}$ that is an orbit of $T$.
  \end{Theorem}
  \vspace{-6mm}
  {\bf Proof.} See~\cite[Th.3]{Supp}

@@

The UAP guarantees that all trajectories will converge to the same trajectory as time moves forward. 
An illustration of this is shown in Fig.~\ref{fig:memloss_conttime} where the trajectory in red seems to lock on to the supposed actual solution in black when the system has the USP.

\begin{figure}[ht]
  \includegraphics[scale=0.35]{Graphs/_Nonlinearity_Fig_response.eps}
  \centering
\captionof{figure}{Input sequence (black) and a coordinate of a simulated solution $(x_0,x_1,\ldots,x_{5000})$ of a RNN  plotted in red (with parameter $a=1$, $\alpha=0.99$ where $g$ has the USP) and blue ($a=1$, $\alpha=1.05$ where $g$ does not have the USP) for randomly generated matrices $A$ and $B$. $B$ has unit spectral radius.  Reproduced from~\cite{Manju_Nonlinearity}. } 
\label{fig:memloss_conttime} 
\end{figure}

@@

\begin{Theorem}
  [\bf Causal Embedding Theorem (adopted from~\cite{Supp})]
  % {\bf (Causal Embedding Theorem.)}
\label{Thm_CET}
	Let $g$ be a driven system with SI-invertibility and the USP. Let $h$ denote the universal semi-conjugacy and $H_2(\overleftarrow{u}) := (h(r\overleftarrow{u}),h(\overleftarrow{u}))$, where $r$ is the right-shift map. 
 Let $(\widehat{U}_T, \widehat{T})$  be the inverse-limit system of a dynamical system $(U,T)$. 
 Then the restriction of $H_2$ to $\widehat{U}_T$ is a topological semi-conjugacy between the inverse-limit system $(\widehat{U}_T, \widehat{T})$ 
and the induced dynamical system  $(Y_T,G_T)$, i.e., the following diagram commutes
\begin{equation} \label{comm_H_CET}
\psset{arrows=->, arrowinset=0.25, linewidth=0.6pt, nodesep=3pt, labelsep=2pt, rowsep=0.7cm, colsep = 1.1cm, shortput =tablr}
 \everypsbox{\scriptstyle}
 \begin{psmatrix}
 \widehat{U}_T & \widehat{U}_T\\%
 Y_T &  Y_T.
 %%%
%  \ncline{1,1}{1,2}^{\widehat{T}} \ncline{1,1}{2,1} <{H_2}
%  \ncline{1,2}{2,2} > {H_2}
%  \ncline{2,1}{2,2}^{G_T}
 \end{psmatrix}
 \end{equation}
or in other words, $(Y_T, G_T)$ is a factor of  $(\widehat{U}_T, \widehat{T})$. Further, if $T:U \to U$ is a homeomorphism, 
then $H_2$ embeds $\widehat{U}_T$ in $X_U \times X_U$, and hence $(Y_T, G_T)$ is conjugate to $(\widehat{U}_T, \widehat{T})$.
\end{Theorem}
\vspace{-6mm}
{\bf Proof.}  May be found as the proof of~\cite[Th.4]{Supp}

@@

\begin{figure}[ht]
  \includegraphics[scale=0.3]{Graphs/_summarypictorial.eps}
  \centering
  \captionof{figure}{Pictorial summary of results obtained up to now and how they overlap. Reproduced from~\cite{SIG25May} }
  \label{fig:pictorialSummary}
\end{figure}
\ednote{Cited SIG25May here, but unsure if bibtex reference is correct}

@@

\begin{Theorem}
  When $x_n$ and $x_{n-1}$ are successive points on a solution obtained for input-orbit of $T$ $\{u_n\}$, then the map $\Gamma: X\times{X}\to{U}$ defined by $(x_{n-1},x_n)\mapsto{u_n}$ exists whenever $G_T$ exists 
\end{Theorem}
\vspace{-6mm}
{\bf Proof.}  See~\cite[Th. 3c]{manjunath2021universal}.

@@

The graph in equation~\ref{comm_H_CET} is then extended to the diagram~\ref{Scomm_imp} below:
